Magnetized accretion disks around Kerr black holes with scalar hair - I. Constant angular momentum

### 2018-06-27 paper_prd.tex
Further changes.

In addition, the detection of gravitational waves from binary BHs~\cite{} and the prospect of observing the first image - the black hole {\it shadow} - of a BH by the Event Horizon Telescope~\cite{Fish:2016} opens the opportunity to test the true nature of BHs and the astrophysical relevance of HBHs. 
Regarding the latter, the source of light in a realistic situation is provided by material from an accretion disk crossing the event horizon of the BH, producing the shadow. Thick accretion disks (or tori) are common in astrophysics, either surrounding the central BHs of quasars and active galactic nuclei or, at a stellar scale, surrounding the compact objects in X-ray binaries, microquasars, and gamma-ray bursts. Motivated by this observational possibility, in this work we build equilibrium solutions of HBHs surrounded by magnetized accretion disks. Our procedure, which combines earlier approaches  
by~\cite{Komissarov:2006,Qian:2009} was presented in~\cite{Gimeno-Soler:2017} for the Kerr BH case. In~\cite{Gimeno-Soler:2017} we built equilibrium sequences of accretion disks  endowed with a purely toroidal magnetic field, assuming a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed. Our immediate goal in the present work is to assess if and how the accretion disk morphology depends on the type of BH considered, either Kerr BHs of varying spins or Kerr BHs with scalar hair (KBHsSH). Moreover, we focus on disks with a constant distribution of specific angular momentum, presenting in a companion paper the non-constant (power-law) case. In subsequent investigations, we will analyze the shadows of the equilibrium models of KBHsSH presented in this work as well as in {\it dynamical} situations.

>>>>

In addition, the detection of gravitational waves from binary BHs~\cite{Abbott2016, Abbott:2016nmj, Abbott:2017vtc, Abbott:2017oio, Abbott:2017gyy} and the prospect of observing the first image - the black hole {\it shadow} - of a BH by the Event Horizon Telescope~\cite{Fish:2016} opens the opportunity to test the true nature of BHs and the astrophysical relevance of HBHs. 
Regarding the latter, the source of light in a realistic situation is provided by material from an accretion disk crossing the event horizon of the BH, producing the shadow. Thick accretion disks (or tori) are common in astrophysics, either surrounding the central BHs of quasars and active galactic nuclei or, at a stellar scale, surrounding the compact objects in X-ray binaries, microquasars, and gamma-ray bursts. Motivated by this observational possibility, in this work we build equilibrium solutions of HBHs surrounded by magnetized accretion disks. Our procedure, which combines earlier approaches  
by~\cite{Komissarov:2006,Qian:2009} was presented in~\cite{Gimeno-Soler:2017} for the Kerr BH case. In~\cite{Gimeno-Soler:2017} we built equilibrium sequences of accretion disks  endowed with a purely toroidal magnetic field, assuming a form of the angular momentum distribution that departs from the constant case considered by~\cite{Komissarov:2006} and from which the location and morphology of the equipotential surfaces can be numerically computed. Our immediate goal in the present work is to assess if and how the accretion disk morphology depends on the type of BH considered, either Kerr BHs of varying spins or Kerr BHs with scalar hair (KBHsSH). Moreover, we focus on disks with a constant distribution of specific angular momentum, presenting in a companion paper the non-constant (power-law) case. In subsequent investigations, we will analyze the shadows of the equilibrium models of KBHsSH presented in this work as well as in {\it dynamical} situations.
